---
title: "ImmGen TF Score Cutoff"
author: Caleb Lareau
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Question

There are 30,218,042 peak-motif pairs in `fimo_cisBP_jmotifs_p4.txt` using `1e-04` as a p-value cutoff. Using a slightly more stringent threshold of `1e-05`, we yield 3,552,978 peak-motif pairs. Does our choice of cutoff affect analysis/interpretation?  

## Analysis strategy

- Import TF binding hits from `fimo_cisBP_jmotifs_p4.txt` into the `chromVAR` analysis environment.
- Per sample/per motif/per threshold, compute deviation z-scores for comparison

## Weak motif associations
Of the 981 unique motifs in our data base, 164 only have association p-values $p_a$ such that $10e-04 > p_a > 10e-05$. In other words, these 164 motifs  have exclusively weak associations and thus would be eliminated (TF scores are `NA`) if we used a more stringent threshold. Below, I show the extreme values of the TF-sample scores for $p_a < 10e-04$ (remember, these scores are `NA` if using a more stringent threshold)--

```
M6353_1.02	lib_7	77.31294
M6353_1.02	lib_216	73.25797
M5273_1.02	lib_10	71.92814
M5273_1.02	lib_207	70.64803
M5273_1.02	lib_13	69.6737
M6353_1.02	lib_142	68.33025
		
M5273_1.02	lib_133	-55.00627
M5273_1.02	lib_135	-51.01178
M5273_1.02	lib_134	-49.59398
M5273_1.02	lib_148	-48.29713
M5273_1.02	lib_175	-46.00564
M5273_1.02	lib_136	-45.72158
```

So, seemingly `M5273_1.02` explains a lot of variability in the data based on the extremes. This motif maps to *Snai2*, which has been [shown to function in hematopoietic progenitor biology (source)](http://gradworks.umi.com/37/27/3727393.html). One can verify that this motif has only  association p-values $p_a$ in the specified range $10e-04 > p_a > 10e-05$ (sanity check). 

```
grep M5273_1.02 fimo_cisBP_jmotifs_p4.txt
```

From this relatively obvious example, it appears that for some motifs, the choice of cutoff does matter, and we may be missing out on relevant biology by selecting a more stringent threshold. 

## Large-scale comparison
Of the 827 motifs that do have at least 1 association p-value $p_a$ such that $p_a < 10e-05$, we see a very nice correlation between the scores as shown in the plot below. 

```{r pressure, echo=FALSE, cache = TRUE}
library(ggplot2)
library(BuenColors)
cd <- readRDS("../output/TFscoreDesnity.rds")
cd$logDensity <- log10(cd$density)
ggplot(cd, aes( x = x,  y = y, color = logDensity)) + theme(plot.subtitle = element_text(vjust = 1), 
    plot.caption = element_text(vjust = 1)) +labs(title = "Sample-Motif TF Score Threshold Comparison", 
    x = "TF Score, p < 10e-04", y = "TF Score, p < 10e-05", colour = "Log Density") + 
    geom_point(size = 0.01) + theme_bw() + scale_color_gradientn(colors = jdb_palette("samba_night"))
```
Each point is a sample-motif pair with TF scores at different binding significance p-values as noted on the axis labels. The log density of the points is denoted in the color.

## Conclusion
Using the more liberal threshold for the peak-motif associations seemingly is the way to go. We'll recover more motifs, and the scores are largely invariant when we use a more stringent threshold when at least 1 motif-association p-value is $p_a < 10e-05$.